---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/snippets)](https://CRAN.R-project.org/package=snippets)
[![R build status](https://github.com/GegznaV/snippets/workflows/R-CMD-check/badge.svg)](https://github.com/GegznaV/snippets/actions)
[![Updated-on](https://img.shields.io/badge/Updated%20on-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

<!-- [![GitHub version](https://img.shields.io/badge/GitHub-v`r packageVersion("snippets")`-brightgreen.svg)](https://github.com/GegznaV/snippets) -->
<!-- [![Updated-on](https://img.shields.io/badge/Updated%20on-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)]() -->
<!-- [![Codecov test coverage](https://codecov.io/gh/GegznaV/snippets/branch/master/graph/badge.svg)](https://codecov.io/gh/GegznaV/snippets?branch=master) -->

# Package `snippets`

<!-- (`r packageVersion("snippets")`) -->
## Installation

<!-- You can install the released version of snippets from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("snippets") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("GegznaV/snippets")
```


## Quickstart


### Install Snippets from "snippets"

```{r eval=FALSE}
# Replace current R and Markdown snippets with those in package "snippets"
snippets::install_snippets_from_package("snippets", type = c("r", "markdown"), backup = TRUE)
```


### More Examples

```{r eval=FALSE}
library(snippets)
```

```{r eval=FALSE}
# Get the name of directory with RStudio snippets
get_rs_snippets_dir()
```

```{r eval=FALSE}
# Open directory with RStudio snippets
open_rs_snippets_dir()
```

```{r eval=FALSE}
# Replace your R and Markdown snippets with those in package "snippets"
install_snippets_from_package("snippets", type = c("r", "markdown"), backup = TRUE)
list_snippet_file_backups()
```

```{r eval=FALSE}
# View and edit file with snippets of certain type: r
edit_rstudio_snippets(type = "r")
```

```{r eval=FALSE}
# View and edit file with snippets of certain type: markdown
edit_rstudio_snippets(type = "markdown")
```


### Create and Clean-up Back-ups

```{r eval=FALSE}
# Create several back up files
backup_rs_snippets(type = "r")
Sys.sleep(1)
backup_rs_snippets(type = "r")
Sys.sleep(1)
backup_rs_snippets(type = "r")
```

```{r eval=FALSE}
list_snippet_file_backups(type = "r")
```

```{r eval=FALSE}
# Remove duplicated back-up files
remove_snippet_backup_duplicates()
```




<!-- 

### Revert to a Certain Version of Back-up 

1. List all back-up files and select the one of interest.
    ```{r eval=FALSE}
    list_snippet_file_backups(type = "r")
    ```
    ```r
    #> c:/.R/snippets/r.snippets
    #> c:/.R/snippets/r.snippets--backup-2019-11-12-033948
    #> c:/.R/snippets/r.snippets--backup-2019-10-31-015042
    ```
2. Restore the back-up of interest, e.g.:
    ```{r eval=FALSE}
    restore_snippets_from_backup("r.snippets--backup-2019-10-31-015042")
    ```
    ```r
    #> v Back-up file was found: 'r.snippets--backup-2019-10-31-015042'
    #> i Snippets' type: r
    #> v Current 'r.snippets' file was backed up:
    #>   'r.snippets' -> 'r.snippets--backup-2020-01-05-012602'
    #> v Snippets were restored from the back-up file:
    #>   'r.snippets--backup-2019-10-31-015042' -> 'r.snippets'.
    ```
-->


# Additional resources

## More on using and writing RStudio snippets

1. [Code Snippets](https://support.rstudio.com/hc/en-us/articles/204463668-Code-Snippets)
   (on RStudio website).
   All information is relevant to RStudio users.
2. [R tip: Save time with RStudio code snippets](https://www.youtube.com/watch?v=h_i__VTSurU) 
   (Case study on YouTube).
3. [Snippets](https://cloud9-sdk.readme.io/docs/snippets) (on Cloud9 SDK website).
   Advanced topics on writing snippets.
   Most sections (but not all) are relevant to RStudio users.


## Similar projects

1. Package [**snippr**](https://github.com/dgrtwo/snippr).


## More snippets

1. [Snippets](https://github.com/dgrtwo/snippets) by @dgrtwo.
1. [Snippets](https://github.com/gadenbuie/snippets) by @gadenbuie.
<!-- 2. [R snippets](https://github.com/Hellerz/hellerz/blob/6180ad13d73c7ff826c9cf514840bbbd899d5873/scripts/ace/snippets/r.snippets) by @Hellerz -->
<!-- 3. [markdown snippets](https://github.com/Hellerz/hellerz/blob/6180ad13d73c7ff826c9cf514840bbbd899d5873/scripts/ace/snippets/markdown.snippets) by @Hellerz -->
<!-- 4. [R snippets](https://github.com/dick7/vimrc/blob/81a78437c9d6f45c3372e6998f4a8a832890c243/sources_non_forked/vim-snippets/snippets/r.snippets) by @dick7 -->
<!-- 5. [markdown snippets](https://github.com/dick7/vimrc/blob/81a78437c9d6f45c3372e6998f4a8a832890c243/sources_non_forked/vim-snippets/snippets/markdown.snippets) by @dick7 -->

<!-- <div style="text-align:right;">`r Sys.Date()`</div> -->
